Integrative forecasting of seasonal influenza A/H3N2 by genotype and phenotype

### 2019-09-02 manuscript/main.tex
Add placeholder forecast figure from Nextstrain

\begin{figure*}[t]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/unadjusted-model-accuracy-and-coefficients-for-simulated-populations.png}
  \caption{Model a) accuracy and b) coefficients for simulated populations of A/H3N2-like viruses.}
  \label{fig:unadjusted_model_accuracy_and_coefficients_for_simulated_populations}
  \end{center}
\end{figure*}

@@

\begin{figure*}[t]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/unadjusted-model-accuracy-and-coefficients-for-natural-populations.png}
  \caption{Model a) accuracy and b) coefficients for natural populations of A/H3N2 viruses.}
  \label{fig:unadjusted_model_accuracy_and_coefficients_for_natural_populations}
  \end{center}
\end{figure*}

@@

\subsection*{Forecasts predict the rise of 3c3.A and A1b clades in February 2020}

>>>>

\begin{figure*}[t]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/unadjusted-model-accuracy-and-coefficients-for-simulated-populations.png}
  \caption{Model a) coefficients and b) accuracy for simulated populations of A/H3N2-like viruses.}
  \label{fig:unadjusted_model_accuracy_and_coefficients_for_simulated_populations}
  \end{center}
\end{figure*}

@@

\begin{figure*}[t]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/unadjusted-model-accuracy-and-coefficients-for-natural-populations.png}
  \caption{Model a) coefficients and b) accuracy for natural populations of A/H3N2 viruses.}
  \label{fig:unadjusted_model_accuracy_and_coefficients_for_natural_populations}
  \end{center}
\end{figure*}

@@

\subsection*{Forecasts predict the rise of A1b/131K and A1b/135K sub-clades in September 2020}

See Fig.~\ref{fig:nextstrain_forecasts}.

\begin{figure*}[t]
  \begin{center}
  \includegraphics[width=\textwidth]{figures/nextstrain-forecasts-for-september-2020.png}
  \caption{Live forecasts on nextstrain.org from our best model for September 2020.}
  \label{fig:nextstrain_forecasts}
  \end{center}
\end{figure*}
